Drawing Math

### 2022-05-15 paper/Paper.tex
fix up notation

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\rationalAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\rationalAngle}[1]{{\theta^j_{#1}}}
\newcommand{\rationalAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\numbToAngle}{\frac{2\pi}{b^j}}
\newcommand{\numbToAngleNoJ}[1]{\frac{2\pi}{b^{#1}}}
\newcommand{\combSingleTermCos}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\sigma^j}
\newcommand{\digSumPeriodicNoJ}{{\sigma}}
\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
\newcommand{\changeTotalOneDim}{\Delta P_{0, T}^d}
\newcommand{\digit}{\mathrm{digit}}
\newcommand{\commonBase}{{\pmb{b}}}
\newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
\newcommand{\numbToCommonNoJ}[1]{\frac{\commonBase}{b^{#1}}}
\newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}
\newcommand{\sinOrCos}{\phi^j}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \sinOrCos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}

@@

Moreover, define $\digSumPeriodic \in \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i).
\end{equation}
In other words, $\digSumPeriodic$ is the digital sum over 
a common decimal sequence period for all rational parameters.

@@

\subsection{Property 1: Restricted Multinomials and Closure}
\label{prop:1}
Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
$A_d$ is the set of rational parameters which are included in determining the position along the $d$th dimension.
Also, for function $f: \Z_\commonBase^{|A_d|} \rightarrow \Z_\commonBase$ and $\{a_1, a_2, ..., a_{|A_d|} \} = A_d$, we will denote
$$
  f\left(\numbToCommonNoJ{a_1} \digSumPeriodicNoJ^{a_1}, \numbToCommonNoJ{a_2}\digSumPeriodicNoJ^{a_2}, ..., \numbToCommonNoJ{a_{A_d}}\digSumPeriodicNoJ^{a_{A_d}}\right)
  = f\left(\digSumPeriodicNoJ\right).
$$

@@

\subsection{Property 2: Root of Restricted Multinomial and Closure}
First note that
$$
\mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\} = 
  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j} \numbToCommon \digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
$$
Let $f_\beta \in \mathcal{M}$ then equal $\sum_{j \in |A_d|} (-1)^{\beta_j}\numbToCommon \digSumPeriodic$.

Then, let
$$
  \mathcal{B} = \left\{\beta: f_\beta(\sigma) = 0\right\}.
$$
Then, if for all
$\beta \in \mathcal{B}$,
$$
\sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      I 
      \commonToAngle 
      \sum_{\ell = 0}^{q}
      \sum_{j \in A_d}
          \left(-1\right) ^ {\beta_{j}}
          \numbToCommon
          \mathrm{digit}(n, b, d, \ell)
  \right) = 0
$$
the turtle will draw a closed shape. While this may seem arbitrary, there is a unique
and interesting geometric interpretation. 
Let a rational decimal sequence $a_1, a_2, ..., a_{\rationalPeriodTotal}$ be equal to
$
\forall \ell \in [\rationalPeriodTotal]
$,
$$
a_\ell = \sum_{j \in A_d}
\left(-1\right) ^ {\beta_{j}}
\numbToCommon
\mathrm{digit}(n, b, d, \ell).
$$
In other words, we are creating a ``common" rational sequence by summing and subtracting
our rational parameters in base $\commonBase$. Then,
if $$
\sum_{q = 0}^{\rationalPeriodTotal - 1}
\exp\left(
    I 
    \commonToAngle 
    \sum_{\ell = 0}^{q}
      a_\ell
  \right) = 0
$$
the turtle closes.
If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
$i \in \set{0, ..., \rationalPeriodTotal - 1}$, then $\exp(I \cdot r_i)$ can be thought of as some point at angle $r_i$ around the 
complex unit circle. Also, note that $r_{i + 1} = r_i + \commonToAngle a_{i+1}$. In otherwords,
$r_i$ denotes some position around the complex unit circle where the subsequent updates
to position are given the $a_i$s, which are a sum and subtraction of rational parameters. Then, if the center of
mass of these points around the unit circle is $0$, the turtle draws a closed shape!
The authors are unsure as to the underlying intuition for why this is true.

For example, say that rational parameters $\frac{22,022}{99,999} = 0.\overline{22022}$ and
$\frac{200}{99,999} = 0.\overline{00200}$ determine the movement in the $x$, $y$, and $z$ axis for $3$ dimensions.
Then, $\sigma^1 = 8$ and $\sigma^2 = 2$. Also note that we are in base 10 so $b^1 = b^2 = \commonBase = 10$.
Also, $f_{00}(8, 2) = 8 + 2 = 10 \equiv 0 \mod 10$. But then, we have that $a = 0.\overline{22222}$.
So then, the ``movement" around the unit circle ends up being evenly spaced out and the center of mass
is 0. Thus, we know that the turtle will close.

>>>>

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\rationalAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\rationalAngle}[1]{{\theta^j_{#1}}}
\newcommand{\rationalAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\numbToAngle}{\frac{2\pi}{b^j}}
\newcommand{\numbToAngleNoJ}[1]{\frac{2\pi}{b^{#1}}}
\newcommand{\combSingleTermCos}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
\newcommand{\changeTotalOneDim}{\Delta P_{0, T}^d}
\newcommand{\digit}{\mathrm{digit}}
\newcommand{\commonBase}{{\pmb{b}}}
\newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
\newcommand{\numbToCommonNoJ}[1]{\frac{\commonBase}{b^{#1}}}
\newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}
\newcommand{\sinOrCos}{\phi^j}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \sinOrCos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\sigma^j}
\newcommand{\digSumPeriodicNoJ}{{\sigma}}

@@

Moreover, for the $j$th rational parameter define $\digSumPeriodic \in \Z_{\commonBase}$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \numbToCommon \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n^j, d^j, b^j, i).
\end{equation}
In other words, $\digSumPeriodic$ is the ``normalized" digital sum over 
a common decimal sequence period for all rational parameters.

@@

\subsection{Property 1: Restricted Multinomials and Closure}
\label{prop:1}
Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
$A_d$ is the set of rational parameters which are included in determining the position along the $d$th dimension.
Also, for function $f: \Z_\commonBase^{|A_d|} \rightarrow \Z_\commonBase$ and $\{a_1, a_2, ..., a_{|A_d|} \} = A_d$, we will denote
$$
  f\left(\digSumPeriodicNoJ^{a_1}, \digSumPeriodicNoJ^{a_2}, ..., \digSumPeriodicNoJ^{a_{A_d}}\right)
  = f\left(\digSumPeriodicNoJ\right).
$$

@@

\subsection{Property 2: Root of Restricted Multinomial and Closure}
First note that
$$
\mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\} = 
  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j} \digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
$$
Let $f_\beta \in \mathcal{M}$ then equal $\sum_{j \in |A_d|} (-1)^{\beta_j}\numbToCommon \digSumPeriodic$.

Then, let
$$
  \mathcal{B} = \left\{\beta: f_\beta(\sigma) = 0\right\}.
$$
Then, if for all
$\beta \in \mathcal{B}$,
$$
\sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      I 
      \commonToAngle 
      \sum_{\ell = 0}^{q}
      \sum_{j \in A_d}
          \left(-1\right) ^ {\beta_{j}}
          \mathrm{digit}(n, b, d, \ell)
  \right) = 0
$$
the turtle will draw a closed shape. While this may seem arbitrary, there is a unique
and interesting geometric interpretation. 
Let a rational decimal sequence $a_1, a_2, ..., a_{\rationalPeriodTotal}$ be equal to
$
\forall \ell \in [\rationalPeriodTotal]
$,
$$
a_\ell = \sum_{j \in A_d}
\left(-1\right) ^ {\beta_{j}}
\numbToCommon
\mathrm{digit}(n, b, d, \ell).
$$
In other words, we are creating a ``common" rational sequence by summing and subtracting
our rational parameters in base $\commonBase$. Then,
if $$
\sum_{q = 0}^{\rationalPeriodTotal - 1}
\exp\left(
    I 
    \commonToAngle 
    \sum_{\ell = 0}^{q}
      a_\ell
  \right) = 0
$$
the turtle closes.
If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
$i \in \set{0, ..., \rationalPeriodTotal - 1}$, then $\exp(I \cdot r_i)$ can be thought of as some point at angle $r_i$ around the 
complex unit circle. Also, note that $r_{i + 1} = r_i + \commonToAngle a_{i+1}$. In otherwords,
$r_i$ denotes some position around the complex unit circle where the subsequent updates
to position are given the $a_i$s, which are a sum and subtraction of rational parameters. Then, if the center of
mass of these points around the unit circle is $0$, the turtle draws a closed shape!
The authors are unsure as to the underlying intuition for why this is true.

For example, say that rational parameters $\frac{22,022}{99,999} = 0.\overline{22022}$ and
$\frac{200}{99,999} = 0.\overline{00200}$ determine the movement in the $x$, $y$, and $z$ axis for $3$ dimensions.
Then, $\sigma^1 = 8$ and $\sigma^2 = 2$. Also note that we are in base 10 so $b^1 = b^2 = \commonBase = 10$.
So, $f_{00}(8, 2) = 8 + 2 = 10 \equiv 0 \mod 10$. But then, we have that $a = 0.\overline{22222}$.
So then, the ``movement" around the unit circle ends up being evenly spaced out and the center of mass
is 0. Thus, we know that the turtle will close.
